Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-10 DGMM2025/paper.tex
fixing intersection algorithm
Add abstract

%
\begin{document}
%
    \title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation}
%
    \titlerunning{Fast and exact visibility on digitized shapes}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
    \author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
    Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
%
    \authorrunning{R. Negro and J.-O. Lachaud}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
    \institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
    \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
%
    \maketitle              % typeset the header of the contribution
%
    \begin{abstract}
        Our abstract
        \keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry}
    \end{abstract}

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $e \gets \max(a, c)$
                    \State $f \gets \min(b, d)$
                    \If{$e < f$}
                        \State $R.append([e, f])$
                    \EndIf
                    \If{$b \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$d \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

>>>>

%
\begin{document}
%
    \title{Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation}
%
    \titlerunning{Fast and exact visibility on digitized shapes}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
    \author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
    Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
%
    \authorrunning{R. Negro and J.-O. Lachaud}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
    \institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
    \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
%
    \maketitle              % typeset the header of the contribution
%
    \begin{abstract}
      Computing visibility on a geometric object requires heavy
      computations since it requires to identify pair of points that
      are visible to each other, i.e. there is a straight segment
      joining them that stays in the close vicinity of the object
      boundary. We propose to exploit a specific representation of
      digital sets based on lists of integral intervals in order to
      compute efficiently the complete visibility graph between
      lattice points of the digital shape. As a quite direct
      application, we show then how we can use visibility to estimate
      the normal vector field of a digital shape in an accurate and
      convergent manner while staying aware of the salient and sharp features of
      the shape.

      \keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry}
    \end{abstract}

@@

    \begin{algorithm}
        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$
                \State $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$
                    \State $[c,d] \gets L[l]$
                    \State $e \gets \max(a, c)$
                    \State $f \gets \min(b, d)$
                    \If{$e \leq f$}\State $R.append([e, f])$
                    \EndIf
                    \If{$b \leq d$}\State $k \gets k+1$
                    \EndIf
                    \If{$d \leq b$}\State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}
